Manuscript

### 2021-08-16 Manuscript/Manuscript_Results.Rmd
small changes in the last plot

```{r Performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1. 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output. The distribution is depicted by the shaded area. The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}
Performance$s1$plot +
    guides(color = 'none', fill = 'none') +
    ggtitle('Session 1') +
    Performance$s2$plot +
    ggtitle('Session 2') &
    theme(
        legend.position = 'bottom'
    ) &
    plot_layout(guides = 'collect')
```

>>>>

```{r Performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1. 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output. The distribution is depicted by the shaded area. The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}

Performance$s1$plot +
	guides(color = 'none', fill = 'none') +
	ggtitle('Session 1') +
	Performance$s2$plot +
	ggtitle('Session 2') +
	theme(
		axis.title.y = element_blank()
	) &
	theme(
		legend.position = 'bottom'
	) &
	plot_layout(guides = 'collect')
```
